Reading Notes

### 2020-06-24 paper.tex
finsihed mazzio

oh this paper is so much better. 
opvs are lightwieght, low cost, flexible. Metrics for evaluating these are PCE, Levelized cost of energy (LCOE) and energy payback time (EPBT).
LCOE is life cycle cost/energy produced. EPBT is how long it takes for a device to pay for itself.
start next time at section 2
inorganic: absorptions of photons with energies greater than the band gap results in free charge carriers that can separate at an p-n junction. they can diffuse under external electric field to electrodes.
organic: lower dielectric constant which prevents screening of the attraction between electrons and holes this results in exciton formation rather than free charges. separation of the exciton requires an acceptor/donor interface. if the exciton doesn't reach an interface it will decay back to ground state resulting in the loss of that energy. donor: large ionization potential acceptor: high electron affinity.
different loss mechanisms are discussed: geminate recombination is where the separated charges recombine across the interface. charge recombination where free charges recombine with unassociates charge carriers in a device.
There is some about electrochem which I am reading but not understanding :( external quantum efficiency is a measure of how much current will be produced by a particular wavelength of light. it depends on the efficiency of photoabsorption, exciton diffusion, charge transfer, charge collection.
CHARGE TRANSFER is not the same as CHARGE TRANSPORT
ASTM reference spectra are used now to characterize and standardize OPV
3. Device architectures
some history about opvs: Tang 1979 introduced the two-component donor acceptor active layer with thermally evaporated small molecules. bilayer structure. limited by exciton diffusion length. 
BHJ with fullerene acceptor reported by Yu in 1995 -still state of the art morphology.
diagrams of different device architectures.
start next time on section 4
materials design (aka the good part :D )
good opv acceptor/donors are solution processable, have appropriate band gaps and energy levels, and long planar pi-stacking for good charge carrier mobilities.
regioregularity (head-tail vs head-head p3ht). Mn is the number average molecular weight of the polymers. weight of all polymers/number of chains. Mw is the molecular weight per unit weight of polymer (accounts for size distribution). dispersity is Mw/Mn.
commonly used materials: initially poly(p-phenylene vinylene) (PPV) was very poplar. It was mixed with PCBM (c60) in first reported BHJ solar cells. now we have shifted away towards poly alkyl thiophenes like p3ht.
p3ht/pcbm was max EQE of 76\%. post processing like thermal annealing with externall electric field produced devices with max PCE of 3.5\%. it has been shown the p3ht and pcbm have strong dependence on regioregularity. longer chains are shown to perform better, due to increased mobility with polymer aggregation.
ways to decrease the band gap have become popular using DA polymers (alternating electron rich and electron poor heterocycles) PCDTBT achieved efficiency of 7.5\%. PTB7 had PCE of 7\% and then over 9\% due to promotion of the quinoidal resonance structure using thienothiophene. quinoidal stabilization improves shortcircuit current (Jsc) and fill factor (FF) which increase EQE and IQE so it has good exciton dissociation, charge transport and extraction.
Some small molecule (not polymer) devices show promise.
fullerenes are commonly used as acceptors. the added groups are to help solubility. pc61bm has limited absorption and deep lumo so it can be improved by using pc71bm which is less symmetric and has more allowed optical transitions. indeneC60 is being used to adjust the LUMO level.
next time section5

>>>>

oh this paper is so much better. 
opvs are lightwieght, low cost, flexible. Metrics for evaluating these are PCE, Levelized cost of energy (LCOE) and energy payback time (EPBT).
LCOE is life cycle cost/energy produced. EPBT is how long it takes for a device to pay for itself.
start next time at section 2
inorganic: absorptions of photons with energies greater than the band gap results in free charge carriers that can separate at an p-n junction. they can diffuse under external electric field to electrodes.
organic: lower dielectric constant which prevents screening of the attraction between electrons and holes this results in exciton formation rather than free charges. separation of the exciton requires an acceptor/donor interface. if the exciton doesn't reach an interface it will decay back to ground state resulting in the loss of that energy. donor: large ionization potential acceptor: high electron affinity.
different loss mechanisms are discussed: geminate recombination is where the separated charges recombine across the interface. charge recombination where free charges recombine with unassociates charge carriers in a device.
There is some about electrochem which I am reading but not understanding :( external quantum efficiency is a measure of how much current will be produced by a particular wavelength of light. it depends on the efficiency of photoabsorption, exciton diffusion, charge transfer, charge collection.
CHARGE TRANSFER is not the same as CHARGE TRANSPORT
ASTM reference spectra are used now to characterize and standardize OPV
3. Device architectures
some history about opvs: Tang 1979 introduced the two-component donor acceptor active layer with thermally evaporated small molecules. bilayer structure. limited by exciton diffusion length. 
BHJ with fullerene acceptor reported by Yu in 1995 -still state of the art morphology.
diagrams of different device architectures.
start next time on section 4
materials design (aka the good part :D )
good opv acceptor/donors are solution processable, have appropriate band gaps and energy levels, and long planar pi-stacking for good charge carrier mobilities.
regioregularity (head-tail vs head-head p3ht). Mn is the number average molecular weight of the polymers. weight of all polymers/number of chains. Mw is the molecular weight per unit weight of polymer (accounts for size distribution). dispersity is Mw/Mn.
commonly used materials: initially poly(p-phenylene vinylene) (PPV) was very poplar. It was mixed with PCBM (c60) in first reported BHJ solar cells. now we have shifted away towards poly alkyl thiophenes like p3ht.
p3ht/pcbm was max EQE of 76\%. post processing like thermal annealing with externall electric field produced devices with max PCE of 3.5\%. it has been shown the p3ht and pcbm have strong dependence on regioregularity. longer chains are shown to perform better, due to increased mobility with polymer aggregation.
ways to decrease the band gap have become popular using DA polymers (alternating electron rich and electron poor heterocycles) PCDTBT achieved efficiency of 7.5\%. PTB7 had PCE of 7\% and then over 9\% due to promotion of the quinoidal resonance structure using thienothiophene. quinoidal stabilization improves shortcircuit current (Jsc) and fill factor (FF) which increase EQE and IQE so it has good exciton dissociation, charge transport and extraction.
Some small molecule (not polymer) devices show promise.
fullerenes are commonly used as acceptors. the added groups are to help solubility. pc61bm has limited absorption and deep lumo so it can be improved by using pc71bm which is less symmetric and has more allowed optical transitions. indeneC60 is being used to adjust the LUMO level.
next time section5
morphology
the ideal is an interpenetrating network of d-a materials with domain sizes on the order of the exciton diffusion length (10 nm). Enough interfacial area to dissociate lots of excitons while maintaining continuous charge transport pathways. Parameters that affect the active layer are solvent donor/acceptor concentrations, thermal annealing times/temps, solvent annealing, additives, and interlayer surface energies. 
solvent - vapor pressure, boiling point, viscosity, polarity, solubility, wettability dictate much of the initial film forming. solute properties like concentration, blend ratio, solubility also important. and finally the method of deposition matters-- high-throughput processing will require alternatives to spin coating but spin-coating is most widely used so it's what this review covers.
switching the solvent in a PPV/PCBM from toluene to chlorobenzene improved performance by nearly three fold! the solvent allowed more mixed/smaller domain sizes. fullerene has better solubility in chlorobenzene.
same active layer compounds in chlorobenzene or toluene, switching the total solute concentration and the ratios had an effect on the morphology but chlorobenzene prevented fullerene aggregation until very high loading.
a study also showed that slow evaporation allowed for separation of p3ht/pcbm but fat allowed for formation of an amorphous glass.
Thermal and solvent annealing allows for larger domains in p3ht/pcbm. annealing increase the hole mobility --> this is the most important factor in increased performance!
Chen (ref 41) studied p3ht/pcbm with GIXD. found that annealing results in bicontinuous network of polymer/fullerene with domains on the order of the exciton diffusion length.
Solvent annealing where layer is annealed under vapor. shown that poor solvents better enchance performance then good solvents. good solvents develop greater self-organization of p3ht -- but the domain were too big. solvent annealing promoted PCBM separatiun to the top of the device.
interpentrating network has been the ideal, but crystalline regions of acceptor donor with mixed amorphous regions is more realistic.
